Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-02-01 paper/letter.tex
conclusiones interesantes

>>>>

%% interpretation
From the optical depth of $10^7$ and the non-detection in the HI line,
we have an upper limit for the size where the Lya emission comes of
$D<0.34$kpc. From this limit and the rotational velocity of $300$ km/s
we have in turn an upper limit for the dynamical mass of $6.6\times
10^{9}$ Msun, which is $\sim 25$ times larger than the $HI$ mass.
